A formal approach but practical approach in train regulation

### 2025-06-05 paper/main.tex
brouillon final  de mon introduction

This contribution finds its origin in a cyber-warefare we are organising for the IT students at the University of Lorraine, see~\cite{CHE}. In the game-play, we have both IT infrastructures and physical systems, with connections between them. On the physical side, we built a small train network that tries to be a good model of real systems.  Our system manages customer informations, train regulation and finally the physical/infrastructure layer. Attackers can hit any of the three parts: disfiguring the site, changing a platform or blocking a signal. Defenders will protect their system, typically via a strict network policy.

@@

>>>>

This contribution finds its origin in a cyber-warefare we are organising for the IT students at the University of Lorraine, see~\cite{CHE}. In the game-play, we have both IT infrastructures and physical systems, with connections between them. On the physical side, we built a small train network that tries to be a good model of real systems.  Our system manages customer informations, train regulation and finally the physical/infrastructure layer. Attackers can hit any of the three parts: disfiguring the website, changing a platform or blocking a signal. Defenders will protect their system, typically via a strict network policy.

@@

For our last research problem, we show that TLA+ may be used to refine a regulation policy. In our first attempts, we had typically some deadlocks issues. We have been able to detect them via TLA+ and then to provide some correction.
